---
title: "Week 4 statistical computing"
author: "MS 276"
date: "September, 2017"
output:
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6)
library(tidyverse); library(okcupiddata)
```

## Write code for the following chart

```{r, echo = FALSE}
sum.profiles <- profiles %>% 
  group_by(sex, orientation) %>% 
  summarise(ave.height = mean(height, na.rm = TRUE), ave.age = mean(age, na.rm = TRUE)) 

ggplot(sum.profiles, aes(orientation, ave.age)) + geom_bar(stat = "identity") + facet_wrap(~sex) + 
  xlab("Orientation") + ylab("Average age") + ggtitle("Average profile age by gender and orientation")
```



## Afterwards

In pairs/groups of 3

1. Install the `fivethirtyeight` package. 

a. First, make a plot of height by age, and facet by pets. 

b. Second, identify average age of each person given their `status` and `orientation`. 

c. Next, identify the percents of each drug response (`drugs`) by drink category (`drinks`). 

2. Think of a question you want to answer that involves at least three of the commands discussed in class

3. Execute the code, and share your HTML file with your professor