---
title: "Homework 1: Stats with R"
author: "Mike Lopez"
date: "September 2017"
output:
  html_document
---

```{r global_options, include=FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(tidyverse)
```


1. Install the `tidyverse` package on your computer, and ensure that you can successfully load the library.  You do not need to show code or output for this answer. 

2. Read Chapters 1 through 4 in R for Data Science, which can be found at ([http://r4ds.had.co.nz/](http://r4ds.had.co.nz/)). You do not need to show code or output for this answer

3. Identify what is wrong with the following code chunks:

-  There are two spellings of `Prof.lopez`

```{r}
Prof.lopez <- "awesome"
Prof.1opez
```

- Some type of sign needed -- addition, multiplication, etc

```{r}
mtcars %>% mutate(gear.times.carb = gear(carb))
```

-  `cyy` is not a variable

```{r}
mtcars %>% filter(cyy == 6)
```


-  Only one equals sign won't work

```{r}
mtcars %>% filter(vs = 0)
```


4. One of the more useful data sets in R is `nycflights13`. Download this package, and ensure that you have it loaded in R. Within that package is a data set called `flights`, which you can take a look at using the following code.

```{r}
library(nycflights13)
dim(flights)
flights %>% summarise(ave.delay = mean(dep_delay, na.rm = TRUE))
```


- How many rows (flights) and columns (variables) are there in the flight data set?

**There are 336776 rows and 19 columns**

- Identify a numerical variable and a character variable in the `flights` data. 

**Answers will vary**

- Identify the average departure delay (`dep_delay`) in the flights data set.

**Average delay is 12.6 minutes**

- Use a tool that we have not yet discussed in class to answer **any** question of interest. As an example, what day of the month do most flights leave on? Do not answer this question, but answer something similar. I encourage you to use outside sources for code!


**Answers will vary**

- Using Chapter 3 of the textbook, show *two* plots using the `flights` data set. They can be any type of plot -- try a few kinds!


**Answers will vary**

- Add better x-axis labels, y-axis labels, a title, and a subtitle to each of your two plots. Note: you only need to show the final versions of the two plots. 


**Answers will vary**

