---
title: "Project requirements - stats with r"
author: "Mike Lopez"
date: "2017"
output:
  pdf_document
---

```{r global_options, include=FALSE, message=FALSE, warning = FALSE}
knitr::opts_chunk$set(eval = FALSE, fig.height = 4, fig.width =5.5)
library(tidyverse)
library(fivethirtyeight)
```

***General instructions***: 

+  Make a new R Markdown file (.Rmd) -- one for each pair of students
+  Change the heading to include your author names
+  By midnight on the night before the presentation, you will email Professor Lopez
with a copy of a knit HTML that you'll use
+  You will scroll through the knit HTML in front of your peers

**Project summary**

R is made awesome by those who build fun things. The goal of the project is to become *experts* at one of the following fun R packages. 

- `rvest` for web scraping

- `lubridate` for working with dates

- `plotly` for interactive plots

- `randomForest` for machine learning tools

- `tidytext` for text mining and sentiment analysis

- `corrr` package for exploring correlations

**Details**

- 10 minute presentation, done in pairs with each person speaking equally

- You *must* use one of the data sets discussed in class. You may also supplement your presentation with outside data. I **strongly** recommend that you do not collect your own data. 

- You *may not* copy and paste code or written word directly from an existing vignette. All code and ideas must be original

- Your written version of the project should not include extensive writing. In other words, most of your presentation should include code, graphs, tables, pictures, etc.

- There must be at least **4** visualizations in your report. Think about how to create awesome and interesting graphics using what we've discussed this year. Note -- pay careful attention to labelling. 

**Additional notes**

- Project packages are awarded on a first come, first serve basis over email. Once two groups have claimed a package, that package is no longer available. 

- Each group must meet with Professor Lopez on 10/16 (9:00 - 11:30 am) to discuss progress and ideas. At that point, each group is responsible for at least *some* progress, which can consist of a few graphs, tables, pages, etc. Lack of progress by this meeting will result in a lower project grade. 

- Points for creativity! Here are all the fun things you can do in R (not required, but possibly interesting) to make your presentation more enjoyable

    - Add an emoji using the `emo` package 
    
    - Add a picture to a plot using `png` package or `magick` package
    
    - Use one of the plotting packages discussed in HW 4 -- these include `ggthemes`, `ggrepel`, `GGally`, `ggridgers`
    
    - Get rid of messages and warnings, and ensure that headings, text, and code are properly formatted.
    
    





```{r}
library(fivethirtyeight)
library(tidyverse)
glimpse(bechdel)
?bechdel
``` 

Refer to the help screen for information regarding each variable. 

## Part I: commands

1. Use R code to answer the following questions

- Identify the movies that passed the Bechdel test in 1980 (using the `binary` variable).

- Identify the movies that grossed more than 2 billion dollars (using 2013 adjusted dollars)

- Identify the percent of movies with `test` result `men-disagree`

- Identify the median domestic gross (using 2013 adjusted dollars) of movies made since 2000 that have passed the Bechdel test (using the `binary` variable). 

2. Replicate the following graphs. Note that to obtain percentages on a bar chart, you can use `geom_bar(position = "fill")`. 


```{r, echo = FALSE, eval = TRUE}
bechdel.sum <- bechdel %>% 
  group_by(year) %>% 
  summarise()

ggplot(bechdel, aes(year, fill = clean_test)) + 
  geom_bar() + 
  labs(title = "# of movies at each Bechdel category", x = "Year", y = "Count")
```

```{r, echo = FALSE, eval = TRUE}

ggplot(bechdel, aes(year, fill = clean_test)) + 
  geom_bar(position = "fill") + 
  labs(title = "% of movies at each Bechdel category", x = "Year", y = "Percent") 

```

3. Review the two charts above. Identify advantages and disadvantages to each visualiation. 

4. Add a line of code to either plot above to change the legend title on the right hand side of the graph (which currently says `clean_test`). You may change to whatever label you think is more appropriate -- and you will need to consult code outside of class to figure this out. 

5. Make histograms of `intgross_2013` and `log(intgross_2013)`. What are the differences?  What are the benefits and disadvantages to working on a log scale?

6. Explore **at least one** of the following tools/packages using `ggplot()`. First, describe what the package is doing (or can do). Second make an interesting graph using the `bechdel` data. Points for creativity!

- [ggthemes, https://cran.r-project.org/web/packages/ggthemes/vignettes/ggthemes.html](https://cran.r-project.org/web/packages/ggthemes/vignettes/ggthemes.html)

- [ggrepel package, https://github.com/slowkow/ggrepel/blob/master/vignettes/ggrepel.md](https://github.com/slowkow/ggrepel/blob/master/vignettes/ggrepel.md)

- [GGally package, http://ggobi.github.io/ggally/](http://ggobi.github.io/ggally/)

- [ggridges, https://cran.r-project.org/web/packages/ggridges/vignettes/gallery.html](https://cran.r-project.org/web/packages/ggridges/vignettes/gallery.html)

- [scale colour brewer, http://ggplot2.tidyverse.org/reference/scale_brewer.html](http://ggplot2.tidyverse.org/reference/scale_brewer.html)

