---
title: "Week 3 Statistical computing"
author: "MS 276"
date: "September, 2017"
fontsize: 11pt 
output:
  pdf_document: default
---

```{r global_options, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE, fig.height = 2.6, fig.width = 5)
```


# okcupiddata

Today we're going to look at cleaned profile data from OkCupid Profile Data for Introductory 
Statistics and Data Science (Journal of Statistics Education, 2015)

According to the packages' Github site, the data contain 

    OkCupid users who were living within 25 miles
    of San Francisco, had active profiles on June 26, 2012, were online in the 
    previous year, and had at least one picture in their profile.

Let's take a look:

```{r}
library(okcupiddata)
names(profiles)
```

With data such as these, there are so many interesting questions we can consider! However, several will involve some data manipulation skills. 


## Data Transformations

We're going to identify five important `dplyr` functions that are appropriate for most data manipulation issues.

\newpage

#### Filter

```{r, eval = FALSE}
profiles %>% filter(drugs == "never")
#
profiles %>% filter(!drugs == "never")
#
profiles %>% filter(drugs == "never", sex == "m")
#
profiles %>% filter(drugs == "never" | sex == "m")
#
profiles %>% filter(drugs == "never", height > 70, sex == "m")
#
profiles %>% filter(drugs %in% c("never", "sometimes"))
#
profiles %>% filter(drugs = "never")
#
dftm <- profiles %>% filter(drugs == "never", height > 70, sex == "m")
```


#### Arrange

```{r, eval = FALSE}
profiles %>% arrange(age)
#
profiles %>% arrange(-age)
#
profiles %>% arrange(age, height)
```



#### Select

```{r, eval = FALSE}
profiles %>% select(age, body_type, diet, drinks)
#
profiles %>% select(age:drinks)
#
profiles %>% select(-age, -diet)
```


#### Mutate

```{r, eval = FALSE}
profiles %>% mutate(drug.free = (drugs == "never"))
#
profiles %>% mutate(feet = height/12, older = age > 40)
#
profiles %>% mutate(feet = floor(height/12), inches = height %% 12)
#
profiles %>% mutate(missing.income = is.na(income)) 
# 
profiles %>% mutate(exists.income = !is.na(income))
```


#### Summaries and grouping

```{r, eval = TRUE}
profiles %>% 
  summarise(ave.age = mean(age), sd.age = sd(age), med.age = median(age), 
            min.age = min(age), max.age = max(age), n.subjects = n())

profiles %>% 
  group_by(sex) %>% 
  summarise(ave.age= mean(age))

profiles %>% 
  group_by(sex, drugs) %>% 
  summarise(ave.height = mean(age), n.subjects = n())

profiles %>% 
  group_by(drugs, sex) %>% 
  summarise(ave.height = mean(age), n.subjects = n())

profiles %>% 
  filter(orientation == "straight", !is.na(drugs)) %>% 
  group_by(drugs, sex) %>% 
  summarise(ave.height = mean(age), n.subjects = n()) %>%
  arrange(ave.height)
```


### Putting it all together

```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
library(nycflights13)
flights.summary <- flights %>% 
  group_by(dest) %>% 
  summarise(ave.delay = mean(arr_delay, na.rm = TRUE), n.flights = n()) %>% 
  filter(n.flights > 100) %>%
  arrange(-ave.delay) %>% 
  slice(1:10)

ggplot(flights.summary, aes(reorder(dest, ave.delay), ave.delay)) + geom_bar(stat = "identity") + 
  labs(title = "Top 10 worst airports to fly into from NYC in 2013", 
       subtitle =  "Among destinations with at least 100 flights", 
          x = "Destination code", y = "Average arrival delay")
```
