---
title: "Week 3 statistical computing"
author: "MS 276"
date: "September, 2017"
output:
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6)
library(tidyverse); library(nycflights13)
```

## Write code for the following chart

```{r, echo = FALSE}
ggplot(flights, aes(dep_delay, air_time, colour = origin, lty = origin)) + 
         geom_smooth() + 
         xlim(0, 200) + 
         facet_wrap(~month) + 
         xlab("Departure Delay") + ylab("Air time") + 
  ggtitle("Air time given departure delay among NYC flights")
```



## Afterwards

In pairs/groups of 3

1. Install the `okcupiddata` package. 

a. First, make a plot of height by age, and facet by pets. 

b. Second, identify average age of each person given their `status` and `orientation`. 

c. Next, identify the percents of each drug response (`drugs`) by drink category (`drinks`). 

2. Think of a question you want to answer that involves at least three of the commands discussed in class

3. Execute the code, and share your HTML file with your professor