---
title: "Week 1 Statistical computing"
author: "MS 276"
date: "September, 2017"
output:
  html_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(dplyr)
library(ggplot2)
```

## Getting started with RStudio and RMarkdown

Go ahead and launch RStudio by going to [r.skidmore.edu](https://r.skidmore.edu/).


### Creating a reproducible lab report

Going forward you should refrain from typing your code directly in the console, and
instead type any code (final correct answer, or anything you're just trying out) in
the R Markdown file and run the chunk using either the Run button on the chunk 
(green sideways triangle) or by highlighting the code and clicking Run on the top 
right corner of the R Markdown editor. If at any point you need to start over, you 
can Run All Chunks above the chunk you're working in by clicking on the down
arrow in the code chunk.


## What's in a Markdown file? 

To get you started, make a new Markdown filerun the following command to load the data.

```{r, eval=TRUE}
mtcars
```

You can do this by

- clicking on the green arrow at the top right of the code chunk in the R Markdown (Rmd) 
file, or
- putting your cursor on this line, and hit the **Run** button on the upper right 
corner of the pane, or
- hitting `Ctrl-Shift-Enter`, or
- typing the code in the console.

This command instructs R to print the `mtcars` data set. 


## Some Exploration

Let's start to examine the data a little more closely. We can access the data in
a single column of a data frame separately using a command like

```{r view-boys}
mtcars$mpg
```

This command will only show the miles per gallon. The dollar
sign basically says "go to the data frame that comes before me, and find the 
variable that comes after me".


## Cheatsheets

Your professor has stored a list of cheatsheets -- [https://github.com/statsbylopez/stats-with-r](https://github.com/statsbylopez/stats-with-r)  -- designed for R and RStudio. This should be your first place to look whenever you have questions. 


## Code chunk options

How can we improve our RMardown file? 

Take a look at the RMarkdown file and identify what the following commands do:

- `message = `
- `warning = `
- `eval = `
- `echo = `
- `include = `


## Resources for learning R and working in RStudio

That was a short introduction to R and RStudio, but we will provide you with more
functions and a more complete sense of the language as the course progresses. 

In this course we will be using R packages called dplyr for data wrangling 
and ggplot2 for data visualization. If you are googling for R code, make sure
to also include these package names in your search query. For example, instead
of googling "scatterplot in R", google "scatterplot in R with ggplot2".

As a final thought, I really liked [this tweet](https://twitter.com/dsquintana/status/904728820904845312). 

Learning R will not come easy, but the payoffs are, um, sweet 

## Building your RStudio skills



#### Packages 

What are packages in R? How do you call a package? What are the most important packages?

####  Arithmetic tools

Give examples of several arithmatic tools that one may want to use. 

####  Storing objects

How to store objects in R? What is a data frame and what does it consist of?  

####  Taking a peek

What do the `glimpse()`, `head()`, `str()`, `dim()` commands

####  Workflow

Describe each of the four panels in an RStudio session. Include how you look at a data frame, your history, and how to ask for help. 





