---
title: "Week 2 Statistical computing"
author: "MS 276"
date: "September, 2017"
output:
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE, fig.height = 2.3, fig.width = 4)
```

## The airlines data set

Today's class is going to focus on a data set containing all flights departing the three primary New York City airports in 2013. After installing the package, we take a look at the data set below. 

```{r, echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
library(nycflights13)
library(tidyverse)
head(flights) %>% print.data.frame()
dim(flights)
set.seed(0)
flights <- flights %>% sample_n(10000)
```

The **codebook** (description of the variables) can be accessed by pulling up the help file:

```{r help}
?flights
```


The `flights` data frame is a massive trove of information. Let's think about 
some graphs that we could make:

- Do later flights (later in the day) have longer or shorter arrival delays?
- How do departure delays vary by month?
- Which NYC airport is the most likely to have a delay of any kind?


### Grammar of graphics

To plot `flights`, the following code puts `dep_time` on the x-axis and `arr_delay` on the y-axis.


```{r}
ggplot(data = flights) + 
  geom_point(aes(x = dep_time, y = arr_delay))
```

- Describe the relationship between departure time and arrival delay. 

- Identify the components of a ggplot graph


### Mappings

```{r}
flights <- flights %>% mutate(vegas = (dest == "LAS"))
ggplot(data = flights) + 
  geom_point(aes(x = dep_time, y = arr_delay, colour = vegas))
```

What are other mappings that we could have used?

### Facets


```{r, fig.width=5}
ggplot(data = flights) + 
  geom_point(aes(x = dep_time, y = arr_delay)) + 
  facet_wrap(~origin)
```


```{r, fig.width=5}
ggplot(data = flights) + 
  geom_point(aes(x = dep_time, y = arr_delay)) + 
  facet_wrap(vegas ~ origin)
```



### Geometric objects

```{r}
ggplot(data = flights) + 
  geom_point(aes(x = dep_time, y = arr_delay)) + 
  geom_smooth(aes(x = dep_time, y = arr_delay))
```

```{r}
ggplot(data = flights, aes(x = dep_time, y = arr_delay)) + 
  geom_point() + 
  geom_smooth()
```



```{r}
ggplot(data = flights, aes(x = vegas, y = dep_delay)) + 
  geom_boxplot()
```


```{r}
ggplot(data = flights, aes(x = carrier)) + 
  geom_bar()
```









