---
title: "Week 2 Statistical computing"
author: "MS 276"
date: "September, 2017"
output:
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6, echo = FALSE)
```


For each plot

1. Write the code that, intuitively, should get you most of the way towards a final plot

2. Identify any new aspects of visualization that you'll need to look up

Use the following code to get started


```{r, echo = TRUE}
set.seed(0)
library(nycflights13)
library(tidyverse)
flights <- flights %>% sample_n(10000)
```

\newpage

1. 

```{r}
ggplot(data = flights, mapping = aes(x = dep_delay, y = arr_delay)) + 
  geom_point() + 
  xlab("Departure Delay") + 
  ylab("Arrival Delay") + 
  ggtitle("Delay times for 10000 flights out of NYC") + 
  facet_wrap(~origin)
```



\newpage

2. 

```{r}
ggplot(data = flights, mapping = aes(x = air_time)) + 
  geom_histogram() + 
  xlab("Air time") + 
  ylab("Number of flights") 
```


\newpage

3. 

```{r}
ggplot(data = flights, mapping = aes(x = dep_delay, y = air_time, colour = origin, lty = origin)) + 
  geom_smooth()  
```


\newpage

4. 

```{r}
ggplot(data = flights, mapping = aes(x = as.factor(month), y = dep_delay)) + 
  geom_jitter()  + 
  annotate("text", x = 12, y = 780, label = "wtf?!?!")
```


\newpage

5. 

```{r}
flights1 <- flights %>% mutate(delayed = arr_delay > 0) 
ggplot(data = flights1, aes(x = as.factor(month))) + 
  geom_bar(aes(fill = delayed), position = "fill") + 
  xlab("Month") + ylab("Delay probabilities")
```


\newpage

6. Using the `flights` data frame, construct code and a rough outline of a plot that you think would be interesting to look at. 

```{r, echo = TRUE}
head(flights) %>% print.data.frame()
```